\documentclass[10pt, a4paper]{article}

\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.5in]{geometry}
\usepackage{fontawesome5}
\usepackage{titlesec}

% Sections formatting
\titleformat{\section}[block]{\bfseries}{}{0pt}{}[\titlerule]
\titleformat{\subsection}[block]{\bfseries}{}{0pt}{}

\begin{document}

\begin{center}
    \textbf{\Huge Gabriel San Martin} \\ \vspace{3pt}

    \small
    \faLinkedin \hspace{.5pt} \href{https://www.linkedin.com/in/gasanmartin}{gasanmartin}
    \vline \hspace{.5pt}
    \faEnvelope \hspace{.5pt} \href{mailto:gabisanmartin12@gmail.com}{gabisanmartin12@gmail.com}
\end{center}

\section{SKILLS}

\begin{itemize}
    \setlength\itemsep{0em}
    \item React, React Native, NextJs, React Query, Storybook, Styled Components
    \item Typescript, Javascript, Jest, Redux, SQL, HTML, Tailwind, CSS
    \item Git, Github, Github Actions, Heroku, CI/CD, Unit Testing
    \item AWS, Firebase, Datadog, Retool
\end{itemize}

\section{EXPERIENCE}

\subsection*{Z League - Frontend Engineer \hfill \small \textit{Feb 2021 - March 2024}}

\begin{itemize}
    \setlength\itemsep{0em}
    \item Enhanced the mobile application by optimizing images, transferring less frequently accessed images to an S3 bucket, and downloading them on demand. Additionally, removed redundant code and dependencies, resulting in a 50\% reduction in the application's bundle size.
    \item Implemented internationalization, thereby enabling the company to reach out to a potential market of approximately 500 million people.
    \item Optimized user experience by enabling seamless background file uploads, empowering users to utilize their devices uninterrupted while files are processed, effectively eliminating wait times.
\end{itemize}

\subsection*{Accelone \hfill \small \textit{Sep 2020 - Feb 2021}}

\subsubsection*{Candidate viewer - Fullstack Engineer}
\begin{itemize}
    \setlength\itemsep{0em}
    \item Executed a complete application migration within one month, resulting in an enhanced client experience when selecting consultants.
    \item Led the implementation from end to end, taking charge of establishing the foundations for both frontend and backend projects.
    \item Crafted a new database architecture, normalized existing data, and scripted the migration process from the old database to the new.
\end{itemize}

\subsubsection*{SousZen - Frontend Engineer}
\begin{itemize}
    \setlength\itemsep{0em}
    \item Integrated Google Maps API to optimize the visualization of company branch locations, resulting in enhanced user experience and improved navigation.
\end{itemize}

\subsubsection*{Chopra - Backend Engineer}
\begin{itemize}
    \setlength\itemsep{0em}
    \item Implemented a custom daemon to monitor an FTP server folder, enhancing the efficiency of sales order processing. This involved processing orders and transforming them into a new format compatible with another daemon. As a result, processing times were significantly reduced, and resource utilization was optimized.
\end{itemize}

\subsection*{Claro - Technical Lead \hfill \small \textit{Jun 2018 - Aug 2020}}
\begin{itemize}
    \setlength\itemsep{0em}
    \item Led the migration and optimization of the coverage website, achieving an impressive 85\% reduction in loading time. This initiative significantly enhanced the user experience for call center staff.
    \item Facilitated the adoption of the new development pipeline among my team members by conducting an online training session, effectively aligning the team with internal processes.
    \item Developed a technical assessment to evaluate developers during interviews. I meticulously analyzed the solutions received, providing my professional insights and opinions to my superiors about the candidates' abilities and suitability for the position. 
\end{itemize}

\subsection*{Mutual Jer\'arquicos - Fullstack developer \hfill \small \textit{Aug 2016 - May 2018}}
\begin{itemize}
    \setlength\itemsep{0em}
    \item Played a key role in the development of the iOS native application MVP, contributing to its conceptualization, design, and implementation phases.
    \item Crafted an efficient online tool for document visualization, seamlessly integrating with an FTP server. This initiative greatly enhanced accessibility, enabling multiple users to effortlessly access over 1000 digitized documents.
\end{itemize}

\section{EDUCATION}

\textbf{National University of the Littoral} \hfill Santa Fe, Argentina \\
\textit{Informatics Engineering (90\%) \hfill March 2010 - Dec 2016} 


\end{document}